### 2021-05-31 docs/manuscript/manuscript.tex
Emphasize role of multiple inputs

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.
\section*{Author summary}
Systems biology is a very fast growing field thanks to the advances in computing and
mathematical modeling of biological systems, and has proven to be a powerful tool that
can help us to understand complex biological processes such as pattern formation in
development. In this article we use an \textit{in silico} approach in order to find and study
the design space of three node Gene Regulatory Networks that are able to produce a
striped pattern of gene expression.

@@

In this study, we used a set of 2061 three-node GRNs selected by a genetic
algorithm to interpret a morphogen signal and respond to it generating a
striped pattern of gene expression in order to analyse the role of network
motifs in this process and its dynamic properties.

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step.
% Author Summary not valid for PLOS ONE submissions.
\section*{Author summary}
Systems biology is a very fast growing field thanks to the advances in computing and
mathematical modeling of biological systems, and has proven to be a powerful tool that
can help us to understand complex biological processes such as pattern formation in
development. In this article we use an \textit{in silico} approach in order to find and study
the design space of multiple input three node Gene Regulatory Networks that are able
to produce a striped pattern of gene expression.

@@

In this study, we used a genetic algorithm to generate a set of 2061 three-node GRNs
including single and multiple input topologies that were able to interpret a morphogen
signal and respond to it generating a striped pattern of gene expression in order to
analyse the role of network motifs in this process and its dynamic properties.
